Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-08-22 manuscript/appC.Rmd
small appendix updates to match ms

Appendix C: Effect of recruitment on IPM uncertainty
=====================================================
In Fig. 4 of the main text where we show the uncertainty around our models' forecasts to a 1% change in climate covariates, the obvious outlier is *Pascopyrum smithii* (PASM). The uncertainty around PASM forecasts from the integral projection model is orders of magnitude larger than for any other species, and is even larger than the uncertainty around the quad-based model forecasts. It turns out that the recruitment parameters we estimate lead to overcompensating density-dependence that is amplified when those parameters are allowed to vary. When we allow all parameters to vary except those associated with recruitment, uncertainty around PASM decreases to levels similar to those associated with other species (Fig. C1). So detailed demographic data is not a cure-all, and can sometimes lead to interesting dynamics when parameter uncertainty is considered.

@@

```{r plot_it, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, fig.width=5, fig.cap="Equilibrium cover and 90% quantiles around the mean prediction from the IPM when model error and parameter uncertainty are propogated through the simulation phase for all vital rates except recruitment.", dependson="plot-options"}
library(plyr)
library(ggplot2)
setwd("~/Repos/MicroMesoForecast/analysis/")
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/cc_rectest/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]

>>>>

Appendix C: Effect of recruitment on IPM uncertainty
=====================================================
In Fig. 4 of the main text where we show the uncertainty around our models' forecasts to a 1% change in climate covariates, the obvious outlier is *Pascopyrum smithii* (PASM). The uncertainty around PASM forecasts from the integral projection model is orders of magnitude larger than for any other species, and is even larger than the uncertainty around the quad-based model forecasts. It turns out that the estimated dispersion parameter for the negative binomial distribution is much higher for PASM than for other species (Appendix B). This is because PASM has higher recruitment rates than the other species and the relationship between number of recruits and quadrat cover (see main text) is weak. So, when we draw parameters from the MCMC chain for our simulations, even larger values for the dispersion parameter are possible. Thus, there can be very large "boom" years where recruitment is high. When we allow all parameters to vary except those associated with recruitment, uncertainty around PASM decreases to levels similar to those associated with other species (Fig. C1).

@@

```{r plot_it, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, fig.width=5, fig.height=3, fig.cap="Equilibrium cover and 90% quantiles around the mean prediction from the IPM when model error and parameter uncertainty are propogated through the simulation phase for all vital rates except recruitment.", dependson="plot-options"}
library(plyr)
library(ggplot2)
setwd("~/Repos/MicroMesoForecast/analysis/")
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/cc_rectest/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]
